### 2014-08-05 analysis/figures/paper_figures.tex
Using mid-basilar for rabbit 10 figure 2.
Comment out alternative versions of figures

\begin{figure}[H]
\begin{center}
\begin{tabular}{cccc}
& VEP & SSAEP 86 Hz & SSVEP 40 Hz \\
\raisebox{-0.5\height}{\rotatebox{90}{Rabbit 8}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_24_04_2014_12_55_56_vep_-crop.pdf}} &
&
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_24_04_2014_12_59_49_ssvep_.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{Rabbit 9}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep_-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40-crop.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{Rabbit 10}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40-crop.pdf}}
\end{tabular}
\caption{At Basilar Tip.} % Figure 2
\end{center}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\begin{tabular}{cccc}
& Rabbit 10 & Rabbit 9 & Rabbit 8 \\
\raisebox{-0.5\height}{\rotatebox{90}{VEP}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep_-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_24_04_2014_12_55_56_vep_-crop.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{SSAEP 86 Hz}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86-crop.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{SSVEP 40 Hz}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_24_04_2014_12_59_49_ssvep_.pdf}}
\end{tabular}
\caption{At Basilar Tip.} % Figure 2
\end{center}
\end{figure}

@@

\setcounter{figure}{2}
\setlength{\tabcolsep}{2pt}
\begin{figure}[H]
\begin{center}
\begin{tabular}{ccccc}
& Basilar Tip & Mid-Basilar & VB Junction & Basilar Tip \\ %& Live Control & Dead Control \\
\raisebox{-0.5\height}{\rotatebox{90}{Resting State}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_15_40-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_24_40-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_33_40-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_36_40-crop.pdf}} \\
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_12_40-crop.pdf}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_40_40-crop.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{VEP}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep_-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep_-crop.pdf}} \\
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr-crop.pdf}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_17_22_22_vep_-crop.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{SSAEP 86 Hz}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_12_19_ssaep_86-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_58_34_ssaep_86-crop.pdf}} \\
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86-crop.pdf}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_17_12_38_ssaep_86-crop.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{SSVEP 40 Hz}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_02_44_ssvep_40-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_38_47_ssvep_40-crop.pdf}}
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40-crop.pdf}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_17_18_01_ssvep_40-crop.pdf}}
\end{tabular}
\caption{Rabbit 10 position dependence.} % Figure 3
\end{center}
\end{figure}
\setlength{\tabcolsep}{6pt}

\setcounter{figure}{2}

\begin{figure}[H] % Transpose of previous
\begin{center}
\begin{tabular}{ccccc}
& Resting State & VEP & SSAEP 86 Hz & SSVEP 40 Hz \\
\raisebox{-0.5\height}{\rotatebox{90}{Basilar Tips}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_15_40-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40-crop.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{Mid-Basilar}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_24_40-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40-crop.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{VB Junction}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_33_40-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep_-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_12_19_ssaep_86-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_02_44_ssvep_40-crop.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{Basilar Tip}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_36_40-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep_-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_58_34_ssaep_86-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_38_47_ssvep_40-crop.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{Live Control}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_12_40-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40-crop.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{Dead Control}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_40_40-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_17_22_22_vep_-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_17_12_38_ssaep_86-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_17_18_01_ssvep_40-crop.pdf}}
\end{tabular}
\caption{Rabbit 10 position dependence.} % Figure 3
\end{center}
\end{figure}

>>>>

%\begin{figure}[H]
%\begin{center}
%\begin{tabular}{cccc}
%& VEP & SSAEP 86 Hz & SSVEP 40 Hz \\
%\raisebox{-0.5\height}{\rotatebox{90}{Rabbit 8}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_24_04_2014_12_55_56_vep_-crop.pdf}} &
%&
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_24_04_2014_12_59_49_ssvep_.pdf}} \\
%\raisebox{-0.5\height}{\rotatebox{90}{Rabbit 9}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep_-crop.pdf}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86-crop.pdf}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40-crop.pdf}} \\
%\raisebox{-0.5\height}{\rotatebox{90}{Rabbit 10}} &
%%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_-crop.pdf}} &
%%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf}} &
%%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40-crop.pdf}}
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_-crop.pdf}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40-crop.pdf}} \\
%\end{tabular}
%\caption{At Basilar Tip for rabbit 8 and 9; at mid-basilar for rabbit 10.} % Figure 2
%\end{center}
%\end{figure}

@@

\begin{figure}[H]
\begin{center}
\begin{tabular}{cccc}
& Rabbit 10 & Rabbit 9 & Rabbit 8 \\
\raisebox{-0.5\height}{\rotatebox{90}{VEP}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep_-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_24_04_2014_12_55_56_vep_-crop.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{SSAEP 86 Hz}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86-crop.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{SSVEP 40 Hz}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_24_04_2014_12_59_49_ssvep_.pdf}}
\end{tabular}
\caption{At Basilar Tip for rabbit 8 and 9; at mid-basilar for rabbit 10.} % Figure 2
\end{center}
\end{figure}

@@

%\setcounter{figure}{2}
%\setlength{\tabcolsep}{2pt}
%\begin{figure}[H]
%\begin{center}
%\begin{tabular}{ccccc}
%& Basilar Tip & Mid-Basilar & VB Junction & Basilar Tip \\ %& Live Control & Dead Control \\
%\raisebox{-0.5\height}{\rotatebox{90}{Resting State}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_15_40-crop.pdf}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_24_40-crop.pdf}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_33_40-crop.pdf}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_36_40-crop.pdf}} \\
%%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_12_40-crop.pdf}} &
%%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_40_40-crop.pdf}} \\
%\raisebox{-0.5\height}{\rotatebox{90}{VEP}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_-crop.pdf}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_-crop.pdf}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep_-crop.pdf}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep_-crop.pdf}} \\
%%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr-crop.pdf}} &
%%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_17_22_22_vep_-crop.pdf}} \\
%\raisebox{-0.5\height}{\rotatebox{90}{SSAEP 86 Hz}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_12_19_ssaep_86-crop.pdf}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_58_34_ssaep_86-crop.pdf}} \\
%%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86-crop.pdf}} &
%%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_17_12_38_ssaep_86-crop.pdf}} \\
%\raisebox{-0.5\height}{\rotatebox{90}{SSVEP 40 Hz}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40-crop.pdf}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40-crop.pdf}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_02_44_ssvep_40-crop.pdf}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_38_47_ssvep_40-crop.pdf}}
%%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40-crop.pdf}} &
%%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_17_18_01_ssvep_40-crop.pdf}}
%\end{tabular}
%\caption{Rabbit 10 position dependence.} % Figure 3
%\end{center}
%\end{figure}
%\setlength{\tabcolsep}{6pt}

%\setcounter{figure}{2}
%\begin{figure}[H] % Transpose of previous
%\begin{center}
%\begin{tabular}{ccccc}
%& Resting State & VEP & SSAEP 86 Hz & SSVEP 40 Hz \\
%\raisebox{-0.5\height}{\rotatebox{90}{Basilar Tips}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_15_40-crop.pdf}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_-crop.pdf}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40-crop.pdf}} \\
%\raisebox{-0.5\height}{\rotatebox{90}{Mid-Basilar}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_24_40-crop.pdf}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_-crop.pdf}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40-crop.pdf}} \\
%\raisebox{-0.5\height}{\rotatebox{90}{VB Junction}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_33_40-crop.pdf}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep_-crop.pdf}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_12_19_ssaep_86-crop.pdf}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_02_44_ssvep_40-crop.pdf}} \\
%\raisebox{-0.5\height}{\rotatebox{90}{Basilar Tip}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_36_40-crop.pdf}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep_-crop.pdf}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_58_34_ssaep_86-crop.pdf}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_16_38_47_ssvep_40-crop.pdf}} \\
%\raisebox{-0.5\height}{\rotatebox{90}{Live Control}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_12_40-crop.pdf}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr-crop.pdf}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86-crop.pdf}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40-crop.pdf}} \\
%\raisebox{-0.5\height}{\rotatebox{90}{Dead Control}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_40_40-crop.pdf}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_17_22_22_vep_-crop.pdf}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_17_12_38_ssaep_86-crop.pdf}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_17_18_01_ssvep_40-crop.pdf}}
%\end{tabular}
%\caption{Rabbit 10 position dependence.} % Figure 3
%\end{center}
%\end{figure}
